The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX
add heatmap

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The relation ship between Priority and Number of Comments}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

\subsection{Result}
In conclusion, we were able to create 4 data sets.
\begin{table} [H]
  \caption{Dataset from Bugzilla}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    Repository&Profit definition&True Cost&True Profit\\
    % &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
    \midrule
    ECLIPSE-I&Log(comments)&50699.70& 3489.64 \\
    FIREFOX-I&Log(comments)& 262945.50& 13025.8 \\
    FIREFOX-II&Priority& 262945.50& 12210 \\
    FIREFOX-III&Priority+Log(comments)& 262945.50& 26332.88 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators. The table also shows the true value of cost & profit that was resolved in 2018. We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.

@@

The main loop of NSGA-II can be described in Algorithm \ref{alg:nsga2}. Initial population is randomly created except one which is greedy solution. The \textit{make-new-pop} function consist of tournament selection, cross-over, and mutation operator which are used to create a child population.

@@

To identify how much our solution are similar to the real world, at third experiment(EX3), we compared the similarity between the real resolved set and the decision vector which is a result of each algorithms.\\

>>>>

\begin{figure*}
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The relation ship between Priority and Number of Comments}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

\subsection{Result}

In conclusion, we were able to create 4 data sets. In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators. The table also shows the true value of cost and profit that was resolved in 2018. We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.

\begin{table} [H]
  \caption{Dataset from Bugzilla}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    Repository&Profit definition&True Cost&True Profit\\
    % &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
    \midrule
    ECLIPSE-I&Log(comments)&50699.70& 3489.64 \\
    FIREFOX-I&Log(comments)& 262945.50& 13025.8 \\
    FIREFOX-II&Priority& 262945.50& 12210 \\
    FIREFOX-III&Priority+Log(comments)& 262945.50& 26332.88 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

@@

The main loop of NSGA-II can be described in Algorithm \ref{alg:nsga2}. Initial population is randomly created except one which is greedy solution. The \textit{make-new-pop} function consist of tournament selection, cross-over, and mutation operator which are used to create a child population. And,

@@

To identify how much our solution are similar to the real world, at third experiment(EX3), we compared the similarity between the real resolved set and the decision vector which is a result of each algorithms.
